---
title: "UK Food Hygiene Ratings"
author: "Barry Bullas"
date: "20/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

list_of_packages <- c("rvest", "dplyr", "httr", "xml2", "jsonlite", "DT")
new_packages <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])]
if(length(new_packages)) install.packages(new_packages)

#Load required packages
lapply(list_of_packages, library, character.only = TRUE)
```

## Aim of the Project

The aim of this project is to be able to retrieve and analyse [Food Hygiene Ratings](http://api.ratings.food.gov.uk/help) for the UK.  

The data will be retrieved using the API which the FSA make available to developers. No sign-up process, API keys, or login details are required at this time to use the service

### Recomended reading

* [API Guidance V1](https://ratings.food.gov.uk/open-data-resources/documents/api-guidance.pdf)
* [API Guidance V2](http://api.ratings.food.gov.uk/help)
* [Terms and conditions of using the data and images](http://www.food.gov.uk/terms-and-conditions).

## Get the authorities
To test using the API with a smaller dataset we will get all of the local authorities.

```{r }
# Message to send to the api as a courtesy.  Helps those running the api contact you if needed
user_text <- 'my@email.address this is a personal project to test retrieving data from the FSA api'

# Static URL for returning all of the authorities
authorities_url <- 'https://ratings.food.gov.uk/authorities/json'

# Get the authorities by passing the GET commmand the URL and the user text
get_authorities_response <- GET(authorities_url, user_agent(user_text))

# Check http_type() of the response
http_type(get_authorities_response)

# Parse returned text with fromJSON()
all_authorities_json <- fromJSON(content(get_authorities_response, as = "text",  encoding = "UTF-8"), simplifyDataFrame = TRUE)

# The authrities are contained within the returned json
all_authorities <- all_authorities_json[["ArrayOfWebLocalAuthorityAPI"]][["WebLocalAuthorityAPI"]]

# Remove Authorities with an id below zero
all_authorities <- all_authorities[all_authorities$LocalAuthorityId  > 0,]

head(all_authorities, 10)
```

## Get Hygiene Ratings

```{r}
# URL for the API
static_url <-
  'http://ratings.food.gov.uk/'
```

